Title

### 2012-02-24 inc/magnetic_lenses/maglens.tex
added specifics about the our lenses (parameters).

\begin{figure}
\centering
\begin{tikzpicture}
  \foreach \n in {0,0.1,...,0.6}{
    \draw [red] (0.75,-0.5) ellipse [x radius=\n,y radius=0.6];
  }
  \foreach \n in {0,0.1,...,0.6}{
    \draw [red] (-0.75,-0.5) ellipse [x radius=\n,y radius=0.6];
  }
  \draw [fill=blue!50] 
    (-0.5,0)
    -- ++(0,2)
    -- ++(-2,0)
    -- ++(0,-5)
      node [pos=0.5,left,align=right] {Magnetic\\Shielding}
    -- ++(2,0)
    -- ++(0,2)
      coordinate [pos=0] (D left)
    -- ++(-0.5,0)
      coordinate [pos=0.5] (S top)
    -- ++(0,-1.5)
    -- ++(-1,0)
    -- ++(0,4)
    -- ++(1,0)
    -- ++(0,-1.5)
    -- ++(0.5,0)
      coordinate [pos=0.5] (S bottom)
    -- cycle
  ;
  \draw [fill=blue!50] 
    (0.5,0)
    -- ++(0,2)
    -- ++(2,0)
    -- ++(0,-5)
    -- ++(-2,0)
    -- ++(0,2)
      coordinate [pos=0] (D right)
    -- ++(0.5,0)
    -- ++(0,-1.5)
    -- ++(1,0)
    -- ++(0,4)
    -- ++(-1,0)
    -- ++(0,-1.5)
    -- cycle
  ;
  \draw [thick, dashed]
    (0,3)
    -- (0,-3)
  ;
  \draw [very thick,<->] 
    (S top) 
    -- (S bottom)
      node [pos=0.5,fill=white] {$S$}
  ;
  \draw [very thick,<->] 
    (D left) 
    -- (D right)
      node [below,pos=0.5,align=center] {$D$\\$(=2R)$}
  ;
  \node [rotate=90] at (-1.6,-0.5) {Windings};
  \node [red,rotate=90] at (1.6,-0.5) {Field Lines};
\end{tikzpicture}
\end{figure}

El-Kareh and El-Kareh \cite{el-kareh_electron_1970} provides an analysis of symmetric lenses with magnetic shielding and a pole-piece in chapter 8, with the most useful information being in section 8.7.

>>>>

\begin{figure}
\centering
\begin{tikzpicture}
  \foreach \n in {0,0.1,...,0.6}{
    \draw [red] (0.75,-0.5) ellipse [x radius=\n,y radius=0.6];
  }
  \foreach \n in {0,0.1,...,0.6}{
    \draw [red] (-0.75,-0.5) ellipse [x radius=\n,y radius=0.6];
  }
  \draw [fill=blue!50] 
    (-0.5,0)
    -- ++(0,2)
    -- ++(-2,0)
    -- ++(0,-5)
      node [pos=0.5,left,align=right] {Magnetic\\Shielding}
    -- ++(2,0)
    -- ++(0,2)
      coordinate [pos=0] (D left)
    -- ++(-0.5,0)
      coordinate [pos=0.5] (S top)
    -- ++(0,-1.5)
    -- ++(-1,0)
    -- ++(0,4)
    -- ++(1,0)
    -- ++(0,-1.5)
    -- ++(0.5,0)
      coordinate [pos=0.5] (S bottom)
    -- cycle
  ;
  \draw [fill=blue!50] 
    (0.5,0)
    -- ++(0,2)
    -- ++(2,0)
    -- ++(0,-5)
    -- ++(-2,0)
    -- ++(0,2)
      coordinate [pos=0] (D right)
    -- ++(0.5,0)
    -- ++(0,-1.5)
    -- ++(1,0)
    -- ++(0,4)
    -- ++(-1,0)
    -- ++(0,-1.5)
    -- cycle
  ;
  \draw [thick, dashed]
    (0,3)
    -- (0,-3)
      node [pos=0,above] {Axis of Electron Microscope Column}
  ;
  \draw [very thick,<->] 
    (S top) 
    -- (S bottom)
      node [pos=0.5,fill=white] {$S$}
  ;
  \draw [very thick,<->] 
    (D left) 
    -- (D right)
      node [below,pos=0.5,align=center] {$D$\\$(=2R)$}
  ;
  \node [rotate=90] at (-1.6,-0.5) {Windings};
  \node [red,rotate=90] at (1.6,-0.5) {Field Lines};
\end{tikzpicture}
\caption{Side-view schematic of a shielded magnetic lens with a pole-piece. The windings (current loops) are contained within the shielding. The magnetic field created by these windings is contained inside the shielding except in the gap.}
\end{figure}

El-Kareh and El-Kareh \cite{el-kareh_electron_1970} provide an analysis of symmetric lenses with magnetic shielding and a pole-piece in chapter 8, with the most useful information being in section 8.7.
They define
\begin{subequations}
\begin{gather}
  k^2 \equiv \frac{e}{8 m V_r} B_0^2 R^2 \\
  \beta \equiv k^2 V_r / (NI)^2 \label{eq:elkareh_k2}
\end{gather}
\end{subequations}
where $N$ is the number of loops, $I$ is the current in a single loop, $B_0$ is the maximum axial magnetic field strength, $R$ is the bore radius and $V_r$ is the relativity corrected acceleration potential, given by
\begin{equation}
  V_r = V ( 1 + \frac{0.978 \cdot 10^{-6}}{\text{Volt}} V )
\end{equation}
They then derive a number of formulae and tabulate the results for a variety of parameters.
Using these tabulated results, and for a choice of parameters one can determine the number of ampere-turns ($NI$) to create a certain focal length.

%TODO check S and D as I seem to remember we have S=0.1in
%TODO need a description of the steel inner tube causing an effective diameter larger than the actual bore
For the UEM, I chose a bore diameter $D$=0.3in and a pole-piece gap $S$=0.5in, for an ratio $S/D=0.6$.
By their table 8.2a this results in $\beta=0.0104$. Then, to create a focal length of 4in ($f/R=16$) table 8.17 gives a value for $k^2 \approx 0.05$.
Finally substituting this value into \ref{eq:elkareh_k2}, with $V=30$kV ($V_r\approx30.88$kV), one can deduce that $NI\approx385$A.

To further ease the burden on the lenses, I actually created two, one placed to either side of the RF cavity. As each has 100 turns, a current of only 2A is needed to drive the two lenses in series.
